---
title: "Lab - 4 Time series Forecasting"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

###clearing the environment and Downloading the required packages
```{r}
#install.packages("r package", repos = "http://cran.us.r-project.org")
#install.packages('forecast')
#install.packages('tseries')
library('forecast')
library('tseries')

```

###Loading and printing the dataset
```{r}
data <- AirPassengers
data

```
###Checking for Unfilled data
```{r}
start(data)
end(data)
sum(is.na(data))
```
###Displaying the statistical summary of the dataset
```{r}

summary(data)
```
###Plotting ‘data’ (No. of Air passengers Vs Year)
```{r}
plot(data)

```
###Plotting 'data' Monthwise
```{r}
tsdata <- ts(data,frequency = 12)
plot(tsdata)
```
###Decomposing the data as multiplicative and storing it as ‘ddata’ and plotting the same.

```{r}
ddata <- decompose(tsdata, "multiplicative")
plot(ddata)
```
###Plotting the following: trend, seasonal and random separately.
```{r}
plot(ddata$trend)
```

```{r}
plot(ddata$seasonal)
```

```{r}
plot(ddata$random)
```

###Performing ADF test for stationarity
```{r}
adf.test(diff(log(data)), alternative="stationary", k=0)

```

###Plotting ACF  
```{r}

acf(diff(log(data)))
```
###Plotting PACF
```{r}
pacf(diff(log(data)))
```

###Model using ARIMA
```{r}
Adata <- arima(log(data), c(0, 1, 1),seasonal = list(order = c(0, 1, 1), period = 12))
Adata


```

