---
output:
  word_document: default
  html_document: default
---
## CSE3506 - Essentials of Data Analytics
  
## Lab Task - 4(11/02/2022)
## Time Series Forecasting
  
### Name: Revanth Bhargava Boyidi
### Reg. No.: 19BCE1177
    
**Store Airpassengers dataset (inbuilt dataset available in ‘R’) in a dataframe named “data”, install packages such as ‘forecast’, ‘tseries’. **
```{r}
setwd("D:\\SEM-VI\\EDA_CSE3506\\Lab\\Lab-4(11-02)_Time Series")
rm(list=ls()) 		#To clear the environment

data <- AirPassengers

#install.packages("r package", repos = "http://cran.us.r-project.org")
#install.packages('forecast')
#install.packages('tseries')
library('forecast')
library('tseries')
```
  
**(i)Display entire dataset**
```{r}
data
```
  
**(ii)Check for unfilled data**
```{r}
length(data[is.na(data) == TRUE])
```
Data doesn't have unfilled data.  
  
**(iii)Display the statistical info of the dataset such as min, max, 1st quartile, 3rd quartile, mean and median.**
```{r}
summary(data)
```
  
**(iv)Plot ‘data’ (No. of Air passengers Vs Year)**
```{r}
plot(data, xlab = 'Year', ylab = 'No. of Air passengers', main = 'No. of Air passengers Vs Year', type='o', pch=20)
```
  
**(v)Plot as timeseries ‘data’ (monthwise)**
```{r}
boxplot(data~cycle(data), xlab = 'Month', ylab = 'No. of Air passengers', main = 'Monthly Air Passengers from 1949 to 1961')
```
  
**(vi)Decompose the data as multiplicative and store as ‘ddata’**
```{r}
ddata <- decompose(data,"multiplicative")
```
  
**(vii)Plot ‘ddata’**
```{r}
autoplot(ddata)
```
  
**(viii)Plot the following: trend, seasonal and random separately.**
```{r}
par(mfrow=c(3,1))
plot(ddata$trend)
plot(ddata$seasonal)
plot(ddata$random)
```
  
**(ix)Perform ADF test for stationarity**
```{r}
adf.test(data, alternative="stationary", k=0)
```
  
**(x)Plot ACF and PACF**
```{r}
par(mfrow=c(1,2))
acf(data)
pacf(data)
```
  
**(xi)Model using ARIMA**
```{r}
auto.arima(data)
```