---
output:
  word_document: default
  html_document: default
---
## CSE3506 - Essentials of Data Analytics
  
## Lab Task - 1(07/01/2022)
## Regression
  
### Name: Revanth Bhargava Boyidi
### Reg. No.: 19BCE1177
    
Setting the path and Importing libraries
```{r}
setwd("D:\\SEM-VI\\EDA_CSE3506\\Lab\\Lab-1(07-01)_Basics")
rm(list=ls()) 		#To clear the environment
library(dplyr)    #dplyr is a library, which has functions related to data analysis
library("ggplot2")  
```
  
Importing Dataset
```{r}
data <- read.csv("CreditWorthiness.csv",header=TRUE)
#data <- sample_n(data,15)
summary(data)
```
  
**Relation between Age of person and amount of credit**
```{r}
ggplot(data,aes(x=age,y=Camt))+geom_point() #To plot
```
  
```{r}
cor.test(data$age,data$Camt)   # to find the correlation value
```
  
**Relation between credit amount and duration of credit**  
```{r}
ggplot(data,aes(x=Camt,y=Cdur))+geom_point() #To plot
```
We can understand from the graph the that as the amount increases, duration also increases. So both are positively correlated.
```{r}
cor.test(data$Camt,data$Cdur)   # to find the correlation value
```
  
**Simple Linear Regression**
```{r}
slr = lm(Camt~Cdur, data) 
summary(slr)
plot(slr$resid)  # Residual plot
qqnorm(slr$resid)   #Q-Q Plot
```
  
**Multiple Linear Regression**
```{r}
mlr = lm(Camt~Cdur+age, data) 
summary(mlr)
plot(mlr$resid)  # Residual plot
qqnorm(mlr$resid)   #Q-Q Plot
```