---
output:
  word_document: default
  html_document: default
---
## CSE3506 - Essentials of Data Analytics
  
## Lab Task - 2(21/01/2022)
## Regression
  
### Name: Revanth Bhargava Boyidi
### Reg. No.: 19BCE1177
    
Setting the path and Importing libraries
```{r}
setwd("D:\\SEM-VI\\EDA_CSE3506\\Lab\\Lab-2(21-01)_Linear Regression")
rm(list=ls()) 		#To clear the environment
library(dplyr)    #dplyr is a library, which has functions related to data analysis
library("ggplot2")  
```
  
**Store first 5 observations (6:00-08:00 ) in ‘data1’, next 10 observations(8:30-13:00) in ‘data2’ and the last 11 observations (13:00-18:00) in ‘data3’.**
```{r}
data1 <- read.csv("data1.csv",header=TRUE)
data2 <- read.csv("data2.csv",header=TRUE)
data3 <- read.csv("data3.csv",header=TRUE)
```
  
**(i) rbind (data1, data2)**
```{r}
rbind(data1, data2)
```
  
**(ii) Store LCZ(TT=0), LCZ(TT=3), LCZ(TT=5), in variables V1, V2 and V3 respectively. Cbind all these three columns.**
```{r}
df <- rbind(data1, data2, data3)
V1 <- df$LCZ_0
V2 <- df$LCZ_3
V3 <- df$LCZ_5
cbind(V1, V2, V3)
```

```{r}
#Importing Dataset
data <- read.csv("Dataset.csv",header=TRUE)
summary(data)
```

```{r}
#Renaming columns
colnames(data)[4] <- "Deg_Temp_Rise"
colnames(data)[5] <- "Pyranometer"
colnames(data)
```
  
**(iii) Plot Time Vs Pyranometer reading of ‘data’**
```{r}
ggplot(data,aes(x=Time, y=Pyranometer))+geom_point() #To plot
```
  
**(iv) Plot Pyranometer reading Vs Two**
```{r}
ggplot(data,aes(x=Pyranometer, y=Two_5))+geom_point() #To plot
```
  
**(v) Plot Pyranometer reading Vs Qact**
```{r}
ggplot(data,aes(x=Pyranometer, y=Qact_5))+geom_point() #To plot
```
  
**(vi) Plot Pyranometer reading Vs degree of temperature rise**
```{r}
ggplot(data,aes(x=Pyranometer, y=Deg_Temp_Rise))+geom_point() #To plot
```
  
**(vii) Determine the best linear fit equation between Pyranometer reading and Two**
```{r}
fit = lm(Pyranometer~Two_5, data)
summary(fit)
```
  
**(viii) Plot the best linear fit**
```{r}
ggplot(data, aes(x=Pyranometer, y=Two_5)) +
    geom_point() +
    geom_smooth(method=lm, se=FALSE)
```
  
**(ix) Determine the Residual Sum of Squares (RSS)**
```{r}
sum((fit$resid)^2)
```
  
**(x) Plot the residuals**
```{r}
plot(fit$resid)  # Residual plot
qqnorm(fit$resid)   #Q-Q Plot
```