---
output:
  word_document: default
  html_document: default
---
## CSE3506 - Essentials of Data Analytics
  
## Lab Task - 3(28/01/2022)
## ANOVA(Augmenting the Thermal Conductivity of PCM Using CuO Nanoparticle)
  
### Name: Revanth Bhargava Boyidi
### Reg. No.: 19BCE1177
    
Setting the path and Importing libraries
```{r}
setwd("D:\\SEM-VI\\EDA_CSE3506\\Lab\\Lab-3(28-01)_Anova")
rm(list=ls()) 		#To clear the environment
library(dplyr)
library("ggplot2")
```
  
```{r}
#Importing Dataset
data <- read.csv("Dataset.csv",header=TRUE)
data
```
  
```{r}
data[is.na(data)] = 0
summary(data)
```
  
**(i)Determine the grand mean, and mean of thermal conductivity.**
```{r}
gm = mean(c(mean.default(data$Analytical_K), mean.default(data$Experimental_K)))
print(paste("Grand Mean:", gm))
am = mean(data$Analytical_K)
print(paste("Mean of Analytical Thermal COnductivity:", am))
em = mean(data$Experimental_K)
print(paste("Mean of Experimental Thermal COnductivity:", em))
```
  
**ANOVA Table**
```{r}
grouped <- data.frame(cbind(data$Analytical_K, data$Experimental_K))
stacked <- stack(grouped)
summary(aov(values ~ ind, data = stacked))
qf(p=0.875, df1=1, df2=14, lower.tail=FALSE)
```
  
**(ii)Sum of Squares between and Sum of Squares within**
Sum of Squares(Between) = 0.022  
Sum of Sqaures(Within) = 11.777  
  
**(iii)Degrees of Freedom (Between, Within and total)**
Degrees of Freedom(Between) = 1 
Degrees of Freedom(Within) = 14
  
**(iv)Mean Squares (Between and Within)**
Mean Squares(Between) = 0.0216  
Mean Squares(Within) = 0.8412  
  
**(v)F_Statistic and F Critical**
F-Statistic = 0.026  
```{r}
fc = qf(p=0.875, df1=1, df2=14, lower.tail=FALSE)
print(paste("F-Crtical:", fc))
```
**(vi)Check, Is Null hypothesize accepted?**
As F-Statistic is larger than F-Critical, **NULL Hypothesis can be rejected**.  
  
**(vii)Plot Vol. Concentration VS Thermal Conductivity**
```{r}
ggplot(data,aes(x=Vol.Concentration, y=Analytical_K))+geom_point()
```
  
**(viii)Plot Vol Concentration Vs % increase in Thermal conductivity –(In bar chart)**
```{r}
ggplot(data,aes(x=Vol.Concentration, y=X.Increase.in.K)) +
  geom_bar(stat="identity") +
  geom_text(aes(label=X.Increase.in.K), vjust=0) +
  geom_text(aes(label=Vol.Concentration), vjust=1)
```
  
**(ix)Error(Measured Value-Analytical Value)**
```{r}
model <- aov(values ~ ind, data = stacked)
sse <- sum((fitted(model) - stacked$values)^2)
print(paste("Sum of Squares Error:", sse))
ssr <- sum((fitted(model) - mean(stacked$values))^2)
print(paste("Sum of Squares Regression:", ssr))
```