---
output:
  word_document: default
  html_document: default
---
## CSE3506 - Essentials of Data Analytics
  
## Lab Task - 5(25/02/2022)
## Logistic Regression
  
### Name: Revanth Bhargava Boyidi
### Reg. No.: 19BCE1177
  
Setting the path and Importing libraries
```{r}
setwd("D:\\SEM-VI\\EDA_CSE3506\\Lab\\Lab-5(25-02)_Logistic Regression")
rm(list=ls()) 		#To clear the environment
```
  
**Importing Dataset**
```{r}
data <- read.csv("Dataset.csv",header=TRUE)
head(data, 10)
```
  
**Understanding the data**
```{r}
dim(data)
summary(data)
sum(is.na(data))
```
There are no missing values in the dataset.
  
**Splitting Dataset into Training data and Test data**
```{r}
split = sort(sample(nrow(data), nrow(data)*.7))
train <- data[split,]
dim(train)
test <- data[-split,]
dim(test)
```
Dataset is divided in the ratio 7:3 for training and testing the model respectively.
  
**Formulating Logistic Regression model**  
```{r}
model <- glm(default.payment.next.month ~., data = train, family = binomial)
summary(model)
```
  
**Predicting Test Data**
```{r}
prediction <- predict(model, test, type="response")
prediction <- ifelse(prediction > 0.5, 1, 0)
head(prediction)
```
Here if the obtained value is is greater the 0.5, then it is assigned as 1, otherwise 0.  
This is done because, logistic regression is done on categorical values only.
  
**Evaluating Test Data**
```{r}
result <- table(prediction, test[,25])
result
accuracy <- sum(diag(result))/sum(result)
accuracy
```
The model developed produces approximately 80% accurate results.
